---
title: "uno: Multiplayer UNO Game in R"
author: "Richi Susil Jacob, Pooja Rajendran Raju, Dhanshree Dhrafani"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{uno: Multiplayer UNO Game in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(uno)
library(dplyr)

```

## Introduction

The uno package lets you simulate a full multiplayer UNO game using realistic rules.

It supports:

-   Full UNO deck generation

-   Dealing hands to players

-   Turn-by-turn play using action and wild cards

-   Winner detection and scoring

## Installation

You can install the development version of uno from GitHub using:

```{r eval=FALSE}
# Install devtools if not already installed
install.packages("devtools")

# Install uno from GitHub
devtools::install_github("MonashARP/game-package-kookaburras")
```

## Create a Full UNO Deck

```{r}
deck <- create_uno_deck()
head(deck)
nrow(deck)  # Should return 108
```

This generates a standard 108-card deck including **number cards** (0–9), **action cards** (Skip, Reverse, +2), and **wild cards** (Wild, Wild Draw 4).

## Deal Hands to Players

```{r}
deal <- deal_hands(deck, n_players = 4)

# Explore hands
names(deal$hands)
deal$hands$Player_1

# View discard pile
deal$discard
```

Each player is dealt 7 cards. The function returns:

- A named list of player hands

- The updated deck

- A starting discard pile with one card

## How Gameplay Works

The game logic is handled through two main functions:

-**play_game()** – Runs the full game from start to finish

-**play_turns_loop()** – Internal engine that manages turns, checks for playable cards, handles actions, and tracks the winner

The game proceeds automatically until one player finishes all cards. If the draw pile runs out before that, the game ends in a draw.

## Simulate a Full Game

```{r}
result <- play_game()

# View winner
result$winner

# Discard pile preview
tail(result$discard)
```

The game runs automatically until one player wins by emptying their hand. All actions (skip, draw, reverse) are handled by the engine.

**Note:** Wild cards (wild, wild_draw4) appear in the discard pile with the color selected by the player who played them. For example, a card with value = "wild" and color = "green" means the player played a wild and chose green.

### Access Individual Results

You can inspect any player's hand:

```{r}
result$hands$Player_2
```

Or check the full discard pile history:

```{r}
result$discard
```

## Available Functions

| Function            | Description                                    |
| ------------------- | ---------------------------------------------- |
| `create_uno_deck()` | Generate a 108-card UNO deck                   |
| `deal_hands()`      | Deal 7 cards to each player                    |
| `play_game()`       | Full simulation: setup + play to winner        |
| `play_turns_loop()` | Internal game loop handling each player's turn |

##  What's Next

 - "UNO" call penalty

 - Deck reshuffling when draw pile is exhausted

 - Optional player interactivity (CLI or Shiny)

 - Usage of more than one deck
