---
title: "uno: Multiplayer UNO Game in R"
author: "Richi Susil Jacob, Pooja Rajendran Raju, Dhanshree Dhrafani"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{uno: Multiplayer UNO Game in R}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(uno)
```

## Introduction

The uno package simulates a full multiplayer UNO game using realistic rules and automatic CPU-driven turns.

It includes:

-   Shuffling and dealing a full UNO deck

-   Turn-based logic with direction reversal

-   Support for action cards (Skip, Reverse, +2, Wild, Wild Draw 4)

-   Automatic winner detection

-   Final scoring with summary output

-   Ideal for teaching game simulations, functional programming, or AI experimentation.

## Installation

You can install the development version of uno from GitHub using:

```{r eval=FALSE}
# Install devtools if not already installed
install.packages("devtools")

# Install uno from GitHub
devtools::install_github("MonashARP/game-package-kookaburras")
```

## Create a Full UNO Deck

```{r}
deck <- create_uno_deck()
head(deck)
nrow(deck)  # Should return 108
```

This generates a standard 108-card deck including **number cards** (0–9), **action cards** (Skip, Reverse, +2), and **wild cards** (Wild, Wild Draw 4).

## Deal Hands to Players

```{r}
deal <- deal_hands(deck, n_players = 4)

# Explore hands
names(deal$hands)
deal$hands$Player_1

# View discard pile
deal$discard
```

Each player is dealt 7 cards. The function returns the hands, updated deck, and one card placed into the discard pile.

## Simulate a Full Game

```{r}
result <- play_game()

# View winner
result$winner

# Discard pile preview
tail(result$discard)
```

The game runs automatically until one player wins by emptying their hand. All actions (skip, draw, reverse) are handled by the engine.

## Score the Game

```{r}
score_game(result)
```

Ranks players based on cards remaining. Winner has 0, others are sorted.

### Visual Summary

```{r}
barplot(score_game(result),
        col = "steelblue",
        main = "Final Card Counts per Player")
```

### Access Individual Results

You can inspect any player's hand:

```{r}
result$hands$Player_2
```

Or check the full discard pile history:

```{r}
result$discard
```

## Available Functions

| Function            | Description                                 |
| ------------------- | ------------------------------------------- |
| `create_uno_deck()` | Generate a 108-card UNO deck                |
| `deal_hands()`      | Deal 7 cards to each player                 |
| `setup_game()`      | Initialize hands, deck, discard, turn state |
| `play_turns_loop()` | Turn-by-turn gameplay engine                |
| `play_game()`       | Full simulation: setup + play to winner     |
| `score_game()`      | Rank players based on final hand sizes      |

##  What's Next

 - "UNO" call penalty

 - Deck reshuffling when draw pile is exhausted

 - Optional player interactivity (CLI or Shiny)

 - Usage of more than one deck
